# Map making


```{r}
#| echo: false
knitr::include_url("maps_slides.html")
```



While we can make simple maps with the included `plot` function from `terra` or `sf`, there is also the `tmap` package that offers some more fancy options in terms of map making. With `tmap` you can build maps from the ground up (quite literally) as you stack different map layers on top of each other. The syntax is quite similar to `ggplot` as you can combine different layers with the `+` operator.

:::{.callout-important}
## tmap

* Install and load the `tmap` package.
* Visualize the land use, elevation and some of the OSM data we used previously.
* Use appropriate color scales!

:::

```{r}
#| echo: false
biomass = terra::rast("../data/raster/Global_Biomass_IPCC.grd")
```

Here is some example code to get you started.

```{r}
#| echo: true

library(tmap)
library(viridis)


tm_shape(biomass, title = "Biomass")+
  tm_raster(col.scale = tm_scale_continuous_log1p(values = viridis(50)))+
  tm_layout(frame = FALSE,
            legend.position = c("left", "bottom"),
            legend.frame = FALSE,
            legend.text.color = "white", legend.title.color = "white",
            legend.reverse = TRUE)


```


